%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  \cventry
  {Research Assisstant}
  {University of California, Los Angeles}
  {Remote}
  {Sep 2024 - Current}
  {
    \begin{cvitems}
    \item {I have been collaborating with Dr. Kallas on a research project. The
        goal is to develop optimization solutions for serverless platforms.
        Currently, our focus is on leveraging batch-call optimization to improve
        performance in an application and language-agnostic way.}
    \item {\textbf{Main Responsibilities:}
        \begin{itemize}[label=-]
        \item Implementing and deploying the solutions for optimization
        \item Evaluating and interpreting the results of experiments
        \end{itemize}
      }
    \item {\textbf{Goals:}
        \begin{itemize}[label=-]
        \item Implement a batching solution for serverless computing platforms
        \item Collect a set of benchmarks of serverless applications that use
          data stores (currently, Redis)
        \item Evaluate our solution’s latency and throughput improvements against baseline
        \end{itemize}
      }
    \end{cvitems}
  }

  \cventry
  {Research Intern}
  {Hong Kong University of Science and Technology}
  {Hong Kong}
  {July 2023 - Oct 2023}
  {
    \begin{cvitems}
    \item {In this internship, I joined Dr. Parreaux Lab (TACO Lab) and worked
        on the MLscript language project.  I contributed to the design and
        implementation of some new features for the MLscript language.}
    \item {\textbf{Main Responsibilities:}
        \begin{itemize}[label=-]
        \item Implementing new features for the MLscript language on top of the
          existing type system
        \end{itemize}
      }
    \item {\textbf{Achievements:}
        \begin{itemize}[label=-]
        \item Developed a deep understanding of type systems theory, including subtyping and type inference
        \item Gained my first research experience by collaborating with talented graduate students in the field
        \end{itemize}
      }
    \end{cvitems}
  }

  \cventry
  {Software Engineer}
  {Hermes Capital Company}
  {Tehran, Iran}
  {Nov 2022 - Apr 2024}
  {
    \begin{cvitems}
      \item {Hermes Capital's core software engineering team excels at providing high-quality algorithmic trading engines as a service.}
      \item {\textbf{Main Responsibilities:}
            \begin{itemize}[label=-]
                \item Designing real-time systems for managing orders on trading
                  exchanges, such as Iranian crypto exchanges and the Tehran Stock Market
                \item Implementing algorithmic trading logic for managing assets
                  in financial markets
            \end{itemize}
            }
      \item {\textbf{Achievements:}
            \begin{itemize}[label=-]
                \item Developing scalable, maintainable, and high-performance systems
                \item Learning the Clojure language, the company’s tech stack,
                  through which I gained practical experience in using
                  functional programming languages.
            \end{itemize}
            }
    \end{cvitems}
  }

  \cventry
  {Software Development Intern}
  {Rahnema College}
  {Tehran, Iran}
  {Aug 2022 - Oct 2022}
  {
    \begin{cvitems}
    % \item {Certificate link:
    %     \href{https://rahnemacollege.com/certificate/mbroughani81ATzvlhQDHBAV_Q}{Here}
    %     }
      \item {During this bootcamp, I learned the principles of software engineering. We worked on a group project (Football Fantasy), building a back‑end endpoint and two client apps (web and Android). During the bootcamp, we learned about software architecture, agile methodology, and essential soft skills required for working in software teams.}
    \end{cvitems}
  }

  % \cventry
  % {Staff member} % Job title
  % {AIChallenge} % Organisation
  % {Tehran, Iran} % Location
  % {Mar 2022 - Aug 2022} % Date(s)
  % {
  %   \begin{cvitems} % Description(s) of tasks/responsibilities
  %     \item {In this university event, as a member of backend team, we developed an django REST app to manage the website of the event. }
  %     \item {\textbf{Main Responsibility:}
  %               \begin{itemize}[label=-]
  %                   \item Back-end development
  %               \end{itemize}
  %               }
  %     \item {\textbf{Achievements:}
  %               \begin{itemize}[label=-]
  %                   \item Learning about REST APIs and how to implement them using django REST framework
  %               \end{itemize}
  %               }
  %   \end{cvitems}
  % }

\end{cventries}
